Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Rename meek → fronting.
Back to ACM alternate style.
Remove ACM copyright block.
Unblind ICSI notary.

% \documentclass{sig-alternate}
\documentclass{IEEEtran}
% \documentclass[11pt]{IEEEtran}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{color}

% Turn off ACM copyright block.
% \toappear{}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{fronting}
\caption{
Domain fronting uses different domain names at different layers.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor,
is the actual destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}

@@

The ``domainless'' fronting style, which omits SNI,
is useful when there is no good front domain known for a web service.
At least one CDN, Fastly, requires the domainless style.
All current web browsers support SNI,
so it is possible that lack of SNI could be used as a distinguisher.
According to our communication with
a representative of
[a blinded organization observing many TLS connections],
\vp{I don't think this needs to be blinded}
% ANON
% the International Computer Science Institute's
% certificate notary~\cite{icsi-notary},
% which observes on the order of 50~million TLS connections daily,
83.5\% of connections used SNI in June~2014.
There are apparently enough connections without SNI
that a censor will at least have to consider seriously
the costs and benefits before deciding to block SNI-less TLS outright.

@@

\bibliographystyle{abbrv}
\bibliography{meek}

>>>>

\documentclass{sig-alternate}
\usepackage{txfonts}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{xspace}
\usepackage{color}

% Turn off ACM copyright block.
\toappear{}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{fronting-diagram}
\caption{
Domain fronting uses different domain names at different layers.
At the plaintext layers visible to the censor---the DNS request and the
TLS Server Name Indication---appears
the front domain \mbox{\textbf{allowed.example}}.
At the HTTP layer, unreadable to the censor,
is the actual destination \mbox{\textbf{forbidden.example}}.
}
\label{fig:fronting}
\end{figure}

@@

The ``domainless'' fronting style, which omits SNI,
is useful when there is no good front domain known for a web service.
At least one CDN, Fastly, requires the domainless style.
All current web browsers support SNI,
so it is possible that lack of SNI could be used as a distinguisher.
According to our communication with
a representative of
the International Computer Science Institute's
certificate notary~\cite{icsi-notary},
which observes on the order of 50~million TLS connections daily,
83.5\% of connections used SNI in June~2014.
There are apparently enough connections without SNI
that a censor will at least have to consider seriously
the costs and benefits before deciding to block SNI-less TLS outright.

@@

\bibliographystyle{abbrv}
\bibliography{fronting}
